First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-07-20 paper/paper.tex
Similarity to functions [Church encoding section in paper]

>>>>

Note that a value of type \ttt{ChurchCoproductMatch (Either a b) r} is very similar to
a function from \ttt{Either a b} to \ttt{r}, with \ttt{church\_coproductMatchEval} allowing
us to apply it to an argument. We can make this fact more explicit in the types with the
change:

\begin{lstlisting}
data ChurchCoproductMatch t where
  ChurchCoproductMatch
    :: (a -> r) -> (b -> r) ->
       ChurchCoproductMatch
          (Either a b -> r)

church_coproductMatchEval
  :: ChurchCoproductMatch (t -> r) ->
     t -> r
church_coproductMatchEval
    (ChurchCoproductMatch f g)
    (Left x)
  = f x
church_coproductMatchEval
    (ChurchCoproductMatch f g)
    (Right y)
  = g y
\end{lstlisting}
